---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sqltargets

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
<!-- badges: end -->

SQL queries (as separate files) occupy an awkward spot within R pipelines. The goal of sqltargets is to offer a shorthand `tar_sql` to reference and execute queries within [a targets project.](https://github.com/ropensci/targets)  

## Installation

You can install the development version of sqltargets like so:

``` r
remotes::install_github("daranzolin/sqltargets)
```

## Example

```{r example}
library(targets)
library(sqltargets)

tar_dir({  # 
# Unparameterized SQL query:
  lines <- c(
    "-- !preview conn=DBI::dbConnect(RSQLite::SQLite())",
    "-- targets::tar_load(data1)",
    "-- targets::tar_load(data2)",
    "select 1 AS my_col",
    ""
  )
  writeLines(lines, "query.sql")
# Include the query in a pipeline as follows.
  tar_script({
    library(tarchetypes)
    library(sqltargets)
    list(
      tar_sql(query, path = "query.sql")
      )
    }, ask = FALSE)
  })
```

## Specifying dependencies

Use `tar_load` or `targets::tar_load` within a SQL comment to indicate query 
dependencies. Check the dependencies of any query 

```{r}
lines <- c(
   "-- !preview conn=DBI::dbConnect(RSQLite::SQLite())",
   "-- targets::tar_load(data1)",
   "-- targets::tar_load(data2)",
   "select 1 AS my_col",
   ""
 )
 query <- tempfile()
 writeLines(lines, query)
 tar_sql_deps(query)
```

## Passing parameters

Pass parameters (presumably from another object in your targets project) from a named list with 
'glue' syntax: `{param}`.

```{r eval = FALSE}
sql_params <- list(age_threshold = 30)
lines <- c(
   "-- !preview conn=DBI::dbConnect(RSQLite::SQLite())",
   "-- tar_load(sql_params)"
   "select id",
   "from table",
   "where age > {age_threshold}",
   ""
 )

tar_sql(query, "path_to_query", query_params = sql_params)
```

## Code of Conduct

Please note that the sqltargets project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

## Acknowledgement

Much of the code has been adapted from [the excellent tarchetypes package.](https://github.com/ropensci/tarchetypes) Special 
thanks to the authors and Will Landau in particular for revolutionizing data pipelines in R.
